Homework 3

### 2019-09-19 hw3/MSimonsHW3.tex
First half of prob 5 for hw 3
Finished number 5 in hw 3

Therefore $M^{-1} = \begin{bmatrix} \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
\frac{-c}{ad-bc} & \frac{a}{ad-bc}\end{bmatrix}$.  Since $M^{-1} \in M_2(\mathbb{Z})$,
each of its elements must be integers.  Its elements can only be
integers if $ad-bc$ evenly divides $a$, $b$, $c$, and $d$. \\
\\
First, assume $a$, $b$, $c$, and $d$ are relatively prime.  If so, then the
only integers that evenly divide all four are $\pm1$.  Therefore
${ad-bc}$ must be $\pm1$. \\
\\
Otherwise, $a$, $b$, $c$, and $d$ are not relatively prime.  Let $m$ be the
greatest common factor of the $a$, $b$, $c$, and $d$.  Now, let $a = mx$,
$b = my$, $c = mz$ and $d = mw$ for some integers $x$, $y$, $z$, and $w$.
As such, $ad - bc = m^2xw - m^yz = m^2(xw - yz)$.  This means that
$m^2$ and $(xw - yz)$ must also be common factors of $a$, $b$, $c$, and $d$.
If $m$ is the greatest common factor, then $m^2 \leq \vertm\vert$.  This is only
possible if $m = 1$.  Likewise, $\vert(xw - yz)\vert \leq \vertm\vert$.
Since $m = 1$, $(xw - yz)$ must be $\pm1$ or $0$, but it can't be $0$ since
$m^2 \cdot 0 = 0$, which can't divide any integer.  Since $m^2 = 1$ and
$xw - yz = \pm1$, $ad - bc = \pm1$.

>>>>

Therefore $M^{-1} = \begin{bmatrix} \frac{d}{ad-bc} & \frac{-b}{ad-bc} \\
\frac{-c}{ad-bc} & \frac{a}{ad-bc}\end{bmatrix}$.  Since $M^{-1} \in M_2(\mathbb{Z})$,
each of its elements must be integers.  Its elements can only be
integers if $ad-bc$ evenly divides $a$, $b$, $c$, and $d$. \\
\\
Let $m$ be the greatest common denominator of $a$, $b$, $c$, and $d$.
Let $a = mx$, $b = my$, $c = mz$, and $d = mw$ for some integers
$x$, $y$, $z$, and $w$ that are not divisible by $m$.
As such $ad-bc = mxmw - mymz = m^2(xw - yz)$.  Since $m$ is the greatest common
denominator and $m^2$ is also a common denominator, $m^2 \leq m$ and this is
only possible if $m = 1$.  Therefore, the greatest common denominator of
$a$, $b$, $c$, and $d$ is 1.  If this is the case, $ad-bc$ must be $\pm1$ since
only $\pm1$ can evenly $a$, $b$, $c$, and $d$.
\\
\\
Next, assume $ad - bc = \pm1$.  By the last proof, $M$ can only be a unit if
$MM^{-1} = I_2$ and $M^{-1} \in M_2(\mathbb{Z})$.  If $ad - bc = 1$, then
$M^{-1} = \begin{bmatrix} d & -b \\ -c & a \end{bmatrix}$ and $MM^{-1} = I_2$.
If $ad - bc = -1$, then $M^{-1} = \begin{bmatrix} -d & b \\ c & -a \end{bmatrix}$
and $MM^{-1} = I_2$.
\\
\\
Thus, $M \in M_2(\mathbb{Z})$ is a unit if and only if $ad - bc = \pm1$.
